\documentclass{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{parskip}
\usepackage{graphicx}

\newcommand\tab[1][1cm]{\hspace*{#1}}

% Margins
\usepackage[top=2.5cm, left=3cm, right=3cm, bottom=4.0cm]{geometry}

\title{User Manual}
\author{Jia Cheng}
\date{January 2020}

\begin{document}
\maketitle

\section{Login/Registration page}
\begin{itemize}
  \item Registration requires unique email (with respect to model-level validation).
  \item I have yet to implement database level restrictions on uniqueness.
  \item After registration/login, a session is created until the browser is closed.
  \item After registration/login , the user will be redirected to the homepage.
  \item If login is successful, the user should see a Welcome, [user’s name] message below the Jumbotron.
\end{itemize}


\section{Header}

\subsection{TodoApp NavBrand}
\begin{itemize}
  \item Clicking this will redirect the user to the homepage.
\end{itemize}


\subsection{Sidebar toggler}
\begin{itemize}
  \item Opens and closes the sidebar
  \item When the sidebar closes, all opened lists(Projects, Tags, Labels, Filters) in the sidebar will be closed.
\end{itemize}


\subsection{Home link}
\begin{itemize}
  \item Redirects to the homepage
\end{itemize}


\subsection{Search bar}
\begin{itemize}
  \item If the current route does not begin with “/tasks”, the user will be redirected to “/tasks” with the relevant search parameters as long the search bar text field is non-empty.
  \item The tasks will be filtered based on whether the task name contains the search term.  Note that search is case-sensitive.
  \item If the user is currently on a “/tasks…” page, with certain filters applied, then the page will filter by both the applied filter as well as the search term.
\end{itemize}


\subsection{Quick Add New Task}
\begin{itemize}
  \item Allows the user to quickly add a task on any page.
\end{itemize}


\subsection{Support}
\begin{itemize}
  \item Links to support page. For decoration.
\end{itemize}


\subsection{Statistics}
\begin{itemize}
  \item A graph showcasing the number of tasks for the next 10 or so days.

\end{itemize}

\subsection{All activities}
\begin{itemize}
  \item An activity log. Records task-related activities, e.g. creation of tasks, and creation/deletion of comments and subtasks. Being a rather basic implementation, each activity item does not actually say exactly which task/subtask/comment is added/deleted.
\end{itemize}

\subsection{Other Users}
\begin{itemize}
  \item Shows a list of other accounts using this app.
\end{itemize}


\subsection{Logout}
\begin{itemize}
  \item Logs the user out and resets the session.
\end{itemize}

\section{Sidebar}
\subsection{All tasks}
\begin{itemize}
  \item View all tasks without filters.
\end{itemize}


\subsection{Projects}
\begin{itemize}
  \item The numbers next to the project indicate the following: Number of projects owned by you/Number of projects shared with you.
  \item Click to open a list consisting of the current projects.
  \item Click the corresponding projects to view the project’s details and the tasks associated with the project.
  \item Projects with a 2-person icon are those that are shared with you.
  \item Projects with a crown icon are projects you have shared with others.
\end{itemize}



\subsection{Tags}
\begin{itemize}
  \item Tags are essentially permanent labels that cannot be deleted.
  \item The tags “Work”, “Social”, “Personal” are created per-user during registration.
\end{itemize}


\subsection{Labels}
\begin{itemize}
  \item Labels work just like tags, however, the user can assign bootstrap colors to the label during label creation.
\end{itemize}

\subsection{Filters}
\begin{itemize}
  \item A filter is a collection of filter fields, which will all be applied in the app view.
  \item The user can specify a start date and end date (at the backend it is required that start date < end date), as well as a group of tags and labels that will become part of the filter.
  
\end{itemize}

\section{Main view}
\subsection{All task view}
\begin{itemize}
  \item Shows all tasks ordered by date.
  \item Under the overdue section, the user is not allowed to create tasks. (However, the user can still create an overdue task using Quick Add Task).
  \item Click add new task to create a task without any tags or labels.
  \item Click on each task to see its details, like subtasks, comments and activity log for that specific task.
  \item Click on the edit button of any task to edit its parameters.
  \item Click on the round checkbox next to any task to toggle its state of completion.
  \item Editing of subtasks and comments is not supported.
\end{itemize}


\subsection{Project View}
\begin{itemize}
  \item Shows a list of tasks (not ordered by date) that are relevant to the project.
  \item Any task created here will belong to the project.
  \item Tasks within each project can be sorted (ascending/descending) based on deadline or priority.
  \item A project can be marked as completed, thereby completing all tasks belonging to the project. Uncompleting a task belonging to a project will automatically uncomplete the project.
  \item Click on the share button on your own projects to share your projects with other users.
\end{itemize}



\subsection{Tag/Label View}
\begin{itemize}
  \item Shows the tasks with the currently selected tag/label.
  \item Any task created here will have the currently selected tag/label.
\end{itemize}


\subsection{Filter View}
\begin{itemize}
  \item Shows the tasks after filtering by the currently selected filter.
  \item Any task created under the filter view will have precisely the tags and labels associated with the current filter. 
\end{itemize}

\section{Deletion}
\begin{itemize}
  \item The following items can be deleted:
  \item Labels (Click on the cross next to the label on the sidebar to delete it)
  \item Projects (In the project view there is a delete project button that will also delete the associated tasks)
  \item Tasks (Click on the circled cross on the left of each task)
  \item Subtasks and Comments (Click of the circled cross)
  \item Note: Deletion of filters is not implemented.
\end{itemize}


\end{document}